\title{
  NAMeC - Team Description Paper \\
  Small Size League RoboCup 2024 \\
  Application of Qualification in Division B
}

\titlerunning{NAMeC - Team Description Paper}

\author{
    M. Bernet, E. Bouvier, A. Calugi, B.Chew, P. Félix, J. Gautier, C. Godinat, C. Gubanski,
    C.Labbé, J. Lindois, T.W. Meunier, E. Miqueu, N. Morera, E. Schmitz, C.A. Vlamynck
}

\authorrunning{E. Schmitz et al.}

\institute{IUT - Université de Bordeaux, Gradignan, France \\
\email{contact@etienne-schmitz.com} (corresponding author)
}

\maketitle

\begin{abstract}
  This paper outlines the latest developments and enhancements undertaken by NAMeC, the RoboCup Small Size League team located in the University of Bordeaux, France.
\end{abstract}

\keywords{RoboCup, Small Size League, embedded systems, path planning, decision making}

\section{Introduction}

\textbf{NAMeC: Aiming for Excellence in RoboCup Small Size League}

Since joining the RoboCup Small Size League in 2018, NAMeC has proudly participated in four major competitions: Montreal, Sydney, Bordeaux, and Eindhoven. Over the years, our team has continuously evolved, with the 2024 season marking a significant milestone as we transitioned to a fully student-led organization. This restructuring has propelled us to achieve our best result yet—4th place at RoboCup 2024.

With our sights set firmly on the podium this year, we have implemented several critical improvements to enhance our performance. These include the development of \textbf{BigBro}, a decision-making algorithm to optimize strategy, and \textbf{Trinamic}, a hardware solution for efficient Field-Oriented Control (FOC). Additionally, we have introduced advanced obstacle avoidance techniques, implemented \textbf{Payload ACK} with TDMA for reliable communication, and designed a new wheel-fixing system to improve stability. Other upgrades include the use of enhanced shell materials for durability and performance, as well as an innovative team color-changing system for improved visibility and adaptability.

With these advancements, NAMeC is determined to make a significant impact at this year’s RoboCup and take another step toward becoming a leader in the RoboCup SSL community.

